Shades of Green

### 2023-09-25 docs/presentations/20230928-sehm_presentation.qmd
add bv trends fig in sehm_pres

import pandas as pd
import numpy as np
from IPython.display import display, Markdown
import matplotlib.pyplot as plt
import matplotlib.ticker as mtick
import seaborn as sns

@@

@@

```{python}
bv_df = pd.read_sql(
    """SELECT bv.sinno_id, bv.bioeconomy_vision, i.year_of_commercialization AS "i.year"
FROM bioeconomy_visions AS bv
JOIN innovation AS i ON i.sinno_id = bv.sinno_id
WHERE bv.sinno_id NOT IN (SELECT sinno_id FROM categorization_notes WHERE notes NOT LIKE "%not forest%")
OR bv.sinno_id NOT IN (SELECT sinno_id FROM bioeconomy_visions WHERE bioeconomy_vision <> 0);
""",
    conn,
)
```

@@

display(
    Markdown(
        f"<span class='text-primary' style='font-size:15rem; font-weight:900'>{bv_df.loc[:, 'sinno_id'].nunique()}</span>"
    )
)

@@

## Bioeconomy Vision by Year

```{python}

plot_bv_trends(bv_year, title="")

>>>>

import pandas as pd
import numpy as np
from IPython.display import display, Markdown

@@

```{python}
# | label: Query bioeconomy visions

bioeconomy_visions = pd.read_sql(
    """
SELECT bv.sinno_id
, codes.Category AS bioeconomy_vision
, i.year_of_commercialization AS "year"
FROM bioeconomy_visions AS bv
JOIN [classification_codes] AS codes ON codes.code = bv.bioeconomy_vision
JOIN innovation AS i ON i.sinno_id = bv.sinno_id
WHERE bv.sinno_id NOT IN (SELECT sinno_id FROM categorization_notes WHERE notes NOT LIKE "%not forest%")
UNION
SELECT DISTINCT(ei.sinno_id)
, 'Bioecology Vision' AS bioeconomy_vision
, i.year_of_commercialization AS "i.year"
FROM eco_innovations AS ei
JOIN innovation AS i ON i.sinno_id = ei.sinno_id
WHERE ei.innovation_type IN (206, 107)
AND ei.sinno_id NOT IN (
  SELECT ei2.sinno_id
  FROM eco_innovations as ei2
  WHERE ei2.innovation_type IN (999, '000')
  );
-- adds recycling innovation to bioecology
""",
    conn,
)

bioeconomy_visions.loc[
    bioeconomy_visions["bioeconomy_vision"] == "Not Bioeconomy",
    ["bioeconomy_vision"],
] = "No Bioeconomy Vision"

uncertain_bioeconomy_visions = bioeconomy_visions.query("bioeconomy_vision == 'Unsure'")

certain_bioeconomy_visions = bioeconomy_visions.loc[
    ~bioeconomy_visions["sinno_id"].isin(uncertain_bioeconomy_visions["sinno_id"]), :
]

count_certain_bioeconomy_visions = (
    certain_bioeconomy_visions.groupby(["year", "bioeconomy_vision"])
    .size()
    .reset_index(name="count")
)

total_certain_bioeconomy_visions = (
    count_certain_bioeconomy_visions.groupby("bioeconomy_vision")
    .agg("sum", numeric_only=True)
    .sort_values("count", ascending=False)
    .reset_index()
)

@@

@@

n_certain_bioeconomy_visions = certain_bioeconomy_visions["sinno_id"].nunique()

display(
    Markdown(
        f"<span class='text-primary' style='font-size:15rem; font-weight:900'>{n_certain_bioeconomy_visions}</span>"
    )
)

@@

## Trends in Bioeconomy Visions{.smaller}
### [No Bioeconomy]{.text-gray-600}, [Bioecology]{style="color:#cc78bc;"}, [Bioresource]{style="color:#de8f05;"} and [Biotechnoloy]{style="color:#029e73;"}{.smaller}

```{python}
# | label: fig-bv_trends
# | fig-cap: '[No Bioeconomy]{.text-gray-600}, [Bioecology]{style="color:#cc78bc;"}, [Bioresource]{style="color:#de8f05;"} and [Biotechnoloy]{style="color:#029e73"}'

color_map = {
    "No Bioeconomy Vision": "rgb(0.8, 0.8, 0.8)",  # Gray
    "Bioecology Vision": "#cc78bc",  # Purple
    "Bioresource Vision": "#de8f05",  # Orange
    "Biotechnology Vision": "#029e73",  # Green
}

def plot_bv_trends_interactive(df):
    traces = []

    for bv, bioeconomy_vision in df.groupby("bioeconomy_vision"):
        traces.append(
            go.Scatter(
                x=bioeconomy_vision["year"],
                y=bioeconomy_vision["count"],
                name=bv,
                mode="lines",
                line=dict(color=color_map[bv]),  # Set line color based on the color_map
            )
        )

    fig = go.Figure(data=traces)
    fig.update_layout(showlegend=False, hovermode="x unified", height=550)
    fig.show()

plot_bv_trends_interactive(count_certain_bioeconomy_visions)
